---
title: "GGGuitar"
author: "Casimir Saternos"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This vignettes is a brief introduction to the ggguitar package.  The graphics are based on ggplot2 and processing on the tidyverse
in general.  

```{r}
library(ggguitar)
library(tibble)
library(ggplot2)
```

Special thanks to Dr. Hadley Wickham and the crew at RStudio  whose work does all of the heavy lifting.

## Examples of Tablature

A chord in ggguitar is represented as a vector containing 6 elements.  Each element represents a string.  A numeric value
represents the fret where a finger is placed.  Zero represents an open string, NA represents a string not played (either skipped or muted). 

A G Major chord can be represented using the following vector.
```{r}
G_M <- c(3, 2, 0, 0, 0, 3)
```

The ggguitar method can be used to create the tablature for this chord.  The numbers in the vector represent fret positions with zeros indicating open strings.  By default the x and y axis are labeled as Strings and Frets along with associated numbers.
```{r}
ggguitar::tablature('G Major', G_M)
```


```{r}
B_M <- c(NA, 2, 4, 4, 4, 2)
C_M <- c(NA, 3, 2, 0, 1, 0)
C_M_bar <- c(8, 10, 10, 9, 8, 8)
D_M <- c(NA, NA, 0, 2, 3, 2)
F_M7 <- c(NA, NA, 3, 2, 1, 0)
e_m <- c(0, 2, 2, 0, 0, 0)
a_m <- c(NA, 0, 2, 2, 1, 0)
b_m <- c(NA, 2, 4, 4, 3, 2)
```



## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))

```{r}
sessionInfo()
```
